---
title: " Leaf mass per area, not total leaf area, drives differences in above-ground biomass distribution among woody plant functional types"
author: "Anna Krystalli & Sinziana Paltineanu"
date: "24/11/2016"
output: html_document
---

***

<br>

# setup

First we install `remake`.

```{r, eval=FALSE}
devtools::install_github("richfitz/remake", dependencies=TRUE)
```

We also need to install `storr`.

```{r, eval=FALSE}
devtools::install_github("richfitz/storr", dependencies=TRUE)
```

Because we only want to install once, we've set the above chunks not to evaluate once the software is installed.

<br>

# download paper resources

We've downloaded the resources associated with the paper and unzipped them. The materials are located in folder `./baadanalysis-master/`. Because the default behaviour of .Rmd is to set the working directory to the directory in which the `.Rmd` is located, we move the .Rmd the `./baadanalysis-master/` directory.

## install missing packages

```{r, eval=FALSE}
remake::install_missing_packages()
```
Indeed, the above command didn't install the `baad.data` package so we run the following code:
```{r, eval=FALSE}
devtools::install_github("richfitz/datastorr")
devtools::install_github("traitecoevo/baad.data")
```


# make paper!

```{r}
remake::make("figures")
```

Oooops. Not working!

Error: `Error in unloadNamespace(package) : 
  namespace ‘stringr’ is imported by ‘evaluate’ so cannot be unloaded
Error in library(p, character.only = TRUE, quietly = TRUE) : 
  Package ‘stringr’ version 1.0.0 cannot be unloaded`

